### 2016-01-29 methods.Rmd
ENH:  More.

The T1 image is then processed via the ANTs brain
extraction and tissue segmentation protocols described in [@Tustison:2014ab] in order to
produce a mask for the brain parenchyma and provide probabilistic estimates of the
cerebrospinal fluid (csf), gray matter, white matter, deep gray matter, brain stem, and
cerebellum.  These provide the ground-truth labels for the first six tissue labels
given above.  The white matter hyperintensities were manually identified by one of the authors
(J. R. S.) using the ITK-SNAP tool [@Yushkevich:2006aa].  Segmentation is performed using
the ANTs Atropos tool [@Avants:2011aa] and
multi-model optimal symmetric shape/intensity templates [@Tustison:2015aa] created from the public
MMRR data set  [@landman2011].

>>>>

The T1 image is then processed via the ANTs brain
extraction and tissue segmentation protocols described in [@Tustison:2014ab] in order to
produce a mask for the brain parenchyma and provide probabilistic estimates of the
cerebrospinal fluid (csf), gray matter, white matter, deep gray matter, brain stem, and
cerebellum.  These provide the ground-truth labels for the first six tissue labels
given above.  The white matter hyperintensities were manually identified by one of the authors
(J. R. S.) using the ITK-SNAP tool [@Yushkevich:2006aa].  Segmentation is performed using
the ANTs Atropos tool [@Avants:2011aa] and
multi-model optimal symmetric shape/intensity templates [@Tustison:2015aa] created from the public
MMRR data set  [@landman2011] (cf Figure X).

![Canonical views of the mutlivariate, bilaterally symmetric template constructed
from the MMRR data set [@landman2011] (only shown are the FLAIR, T1, and T2 modalities---
the components relevant for this work).  Template construction is detailed in
[@Tustison:2015aa].  These images are important for certain intensity-based
features.](Figures/MMRR.png)
